\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-05-28 write_up/mixfishsim_ecolmod.tex
Revisions

The consequences of different spatial aggregations of the data are shown in
Figure \ref{fig:1}, which represents the aggregation of catch from each of the
data sources over a ten year period (to average seasonal patterns) at different
spatial resolutions. \\

@@

Figure \ref{fig:2} shows the consequences of different temporal aggregations of
the data over a three year period, with 156 weekly (top), 36 monthly (middle)
and 3 yearly (bottom) catch compositions from across an aggregated 20 x 20
area. \\

@@

\begin{figure}[!ht]
	\includegraphics[width =\linewidth]{../analysis/Data_Aggregation_time_Rev}
	\caption{Data aggregation at different temporal resolutions over a
		three year period}
	\label{fig:2}
\end{figure}

>>>>

The consequences of different spatial aggregations of the data are shown in
Figure \ref{fig:1}, which represents the aggregation of catch from each of the
data sources over a ten-year period (to average seasonal patterns) at different
spatial resolutions. \\

@@

Figure \ref{fig:2} shows the consequences of different temporal aggregations of
the data over a ten-year period, with weekly (top), monthly (middle) and yearly
(bottom) catch compositions from across an aggregated 20 x 20 area. \\

@@

\begin{figure}[!ht]
	\includegraphics[width =\linewidth]{../analysis/Data_Aggregation_time_Rev}
	\caption{Data aggregation at different temporal resolutions over a
		ten-year period}
	\label{fig:2}
\end{figure}
